Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2018-12-07 v1-task-relevance-cspc.Rmd
First Draft

```{r figure1, echo=FALSE, fig.cap='(ref:figure1)', out.width = "75%", fig.align="center"}
knitr::include_graphics("images/Task.jpg")
```

@@

```{r figure2, echo=FALSE, fig.cap='(ref:figure2)', out.width = "75%", fig.align="center"}
knitr::include_graphics("images/E1_bar.jpg")
```

@@

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$countProp_trialCongruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant,  showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, $\eta$~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, $\eta$~p~2 = .01. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

>>>>

```{r figure1, echo=FALSE, fig.cap="(ref:figure1)", fig.width=6.7,fig.height=4.51}
knitr::include_graphics("images/Task.jpg")
```

@@

```{r figure2, echo=FALSE, fig.cap="(ref:figure2)", fig.width=6.875, fig.height= 4}
figure2
```

@@

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context_Congruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`, showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r RT_ANOVA$Task_Relevant_Context_Congruency`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
